---
title: "Vignette for MercurioRyanTools"
author: "Ryan Mercurio"
date: "'3.7.2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



This package is my submission for Homework 3 in STAT 3701.

Included in this package are all the functions I have written for class quizzes and homeworks so far.
I have omitted redundant functions (e.g. non-GIEMO functions that had GIEMO equivalents).

The first three functions (plottr, filtr, and mylogl) were included in the package submitted for Quiz 2. I have left them in with minimal revision.

Below I briefly demonstrate each function and each attached dataset.

\
\
\
\
\
\/

#Package Functions



##plottr(dataset,...)

plottr plots the first two columns of a dataframe, with the first column as x and the second as y. The ... argument is passed to geom.point(...) so that color,size, etc. of the data may be changed (I would advise against choosing yellow).



```{r, warning=F}
library("MercurioRyanTools")
library(dplyr)
plottr(data1)

x <- data2
y <- 1:30
plotdata <- data.frame(y, x)
plottr(plotdata)
plottr(plotdata, col="yellow", size = 10)

```



##filtr(dataset, col, ...)

  filtr will return a specific column from a given dataset. This is really just a wrapper for dplyr::select(). Can call by column number or by column name.
  
```{r}
 
  
  a <- c(4,5,-14)
  b <- rnorm(3)
  
  c <- data.frame(a,b)

  filtr(c,col = 1)
  
  all.equal(filtr(c, col = 'b'), filtr(c, col = 2))
```

##mylogl(x, func, interval)

  This function takes a numerical vector $x$, an approximate distribution $func$ and estimates the maximum log-likelihood estimator on a specified range $interval$. 
  
  $func$ is a user-defined function of form $function(theta,x)$ where $theta$ is a parameter and $x$ is the numerical vector.
 
###Example functions for argument "fun":

```{r}
f1 <- function(theta,x)
    {dgamma(x, shape = theta, log = TRUE)}

f2 <- function(theta,x)
    {dcauchy(x, location = theta, log = TRUE)}

f3 <- function(theta,x)
    {dbinom(x, 20, prob = 1 / (1 + exp(- theta)), log = TRUE)}
```
###Calling mylogl()
```{r}

#Gamma
mylogl (x = rgamma(20,shape = 1), f1, interval = c(0.1,10))
#Cauchy
mylogl (x = rcauchy(20, loc = 5), f2, interval = c(-10,10))
#Binomial
mylogl (x = rbinom(n = 20,size = 20, prob = .80), f3, interval = c(-10,10))



```
##myapply(X, MARGIN, FUN,...)

  This function works like $apply()$, but is more limited, since the 'MARGIN' argument must be equal to 1 or 2.
  
  myapply applies a user-supplied function 'FUN' to either all rows ('MARGIN = 1') or all columns ('MARGIN = 2') of some object 'X' 


```{r}
app1 <- data.frame(1:30,2:31)
myapply(app1, 1, sum)
myapply(app1, 2, sum)



myapply(app1, 2, function (x)mylogl(x=x,func = f1, interval = c(0.1,30)))

```
##meanvarsd(d)

Finds the mean, variance, and standard deviation of a discrete probability distribution 'd'.  
d\$x should list values with corresponding weights listed in d\$p.

The weights in d\$p must sum to 1.

Returns mean, variance, and standard deviation in that order as a vector of length 3. Works only on data frames
```{r}
x <- 1:4
p <- c(.1,.2,.3,.4)
dist1 <- data.frame(x,p)

meanvarsd(dist1)

```
##%matlc%
A novelty matrix calculator for the expression $X^T A^{-1} X$

Where the transpose of $X$ is multiplicable by the inverse of $A$.

Here we have a candidate for $A$:
```{r}
data4[[1]]
```

And a candidate vector for $X$:
```{r}
data4[[2]]
```
The function is used like so:
```{r}
data4[[1]] %matcalc% data4[[2]]
```

##mstandardize(M)
  This simple function standardizes the columns of a matrix in relation to the column's mean and standard deviation.
  
  This should work for any matrix so long as no column has a standard deviation of 0.
```{r}
data3
```
  This matrix should provide a sufficient example.
```{r}
round(mstandardize(data3), digits = 2)
```
\
\
\
\
\
\
\
\/



#Package Data

Attached data comes from Charlie's 3701 web files. 

##data1

Discrete probability distribution. Two columns: x and p.
```{r, echo=FALSE, results='asis'}
knitr::kable(head(data1))
```

##data2

Data vector of length 30. Follows cauchy distribution.
```{r, echo=F}
knitr::kable(head(data2))
```

##data3

6x4 matrix.
```{r, echo=F}
knitr::kable(head(data3))
```

##data4

List with two items. data4[[1]] is a 3x3 matrix. data4[[2]] (apparently called 'x') is a numerical vector of length 3.
```{r, echo=F}
knitr::kable(head(data4))
```


