---
title: "Vignette for MercurioRyanTools"
author: "Ryan Mercurio"
date: "'3.7.2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



This package is my submission for Homework 3 in STAT 3701.

Included in this package are all the functions I have written for class quizzes and homeworks so far.
I have omitted redundant functions (e.g. non-GIEMO functions that had GIEMO equivalents).

The first three functions (plottr, filtr, and mylogl) were included in the package submitted for Quiz 2. I have left them in with minimal revision.

Below I briefly demonstrate each function and each attached dataset.

\
\
\
\
\
\/

#Package Functions



##plottr(dataset,...)

plottr plots the first two columns of a dataframe, with the first column as x and the second as y. The ... argument is passed to geom.point(...) so that color,size, etc. of the data may be changed (I would advise against choosing yellow).



```{r, warning=F}
library("MercurioRyanTools")
library(dplyr)
plottr(data1)

x <- data2
y <- 1:30
plotdata <- data.frame(y, x)
plottr(plotdata)
plottr(plotdata, col="yellow", size = 10)

```



##filtr(dataset, col, ...)
##mylogl(x, func, interval)
##myapply(X, MARGIN, FUN,...)
##meanvarsd(d)
##%matlc%
##mstandardize(M)


\
\
\
\
\
\
\
\/



#Package Data

Attached data comes from Charlie's 3701 web files. 

##data1

Discrete probability distribution. Two columns: x and p.
```{r, echo=FALSE, results='asis'}
knitr::kable(head(data1))
```

##data2

Data vector of length 30. Follows cauchy distribution.
```{r, echo=F}
knitr::kable(head(data2))
```

##data3

6x4 matrix.
```{r, echo=F}
knitr::kable(head(data3))
```

##data4

List with two items. data4[[1]] is a 3x3 matrix. data4[[2]] (apparently called 'x') is a numerical vector of length 3.
```{r, echo=F}
knitr::kable(head(data4))
```


